\chapter{Results}

Table \ref{tab:performances} summarizes the models' performances in terms of means and standard deviations for each metric, both estimated over all 33 districts and 52 train-test splits, for predictions of CF.
The choice of metrics was made in accordance with the use case requirements, as described in chapter \ref{chap:experiments}.
Table \ref{tab:trainingtimes} show the overall training times for each method, normalized by the number of districts (33) and the number of train-test splits (52).

The most relevant finding was that GWNet models outperformed the statistical counterpart models by more than $38\%$ in terms of RMSE while also presenting the shortest training times.
Also, only GWNet presents a significant improvement over the naïve model, while the relative error $MdRAE$ remained all close to 1.0 (no improvement) for all other methods.
NBEATS, the univariate counterpart in machine learning in this investigation, presented generally better results than the statistical methods, with more than $25\%$ smaller RMSE.
This came, however, at the expense of significantly higher computational costs, with up to 2 orders of magnitude higher than the others in terms of training time.

We emphasize that the usage of $GPUs$ when training GWNet, as well as the absence of parallelization when statistical training models, probably biased the assessment of computational costs.
In their current implementation, however, which is mostly close to the base implementations currently available, GWNet presented the best scalability among the four approaches.
It was observed that, while the training time for the univariate approaches increased linearly with the number of districts, times for GWNet scaled sublinearly, even when no $GPU$ acceleration was used.


\begin{table}
\centering
\caption{Performances of different forecasting approaches for the wind power generation use case. Metrics are calculated on basis of CF values at test timestamps.}
\label{tab:performances}
\resizebox{0.8\linewidth}{!}{%
\begin{tabular}{c|rrr}
\toprule
Model  & \multicolumn{1}{c}{MAE} & \multicolumn{1}{c}{RMSE} & \multicolumn{1}{c}{MdRAE}  \\
\hline
ARIMA  & 0.143 (0.078)           & 0.174 (0.093)            & 0.963 (0.563)              \\
HW-ES  & 0.168 (0.083)           & 0.228 (0.083)            & 0.966 (0.244)              \\
NBEATS & 0.105 (0.050)           & 0.131 (0.066)            & 0.984 (0.389)              \\
GWNet  & \textbf{0.086 (0.045)}  & \textbf{0.107 (0.056)}   & \textbf{0.812 (0.335)}     \\
\bottomrule
\end{tabular}
}
\end{table}

\begin{table}
\centering
\caption{Computation time at training, in $s/(districts \cdot splits)$. Univariate models ARIMA, HW-ES and NBEATS were trained without paralellization. GWNet models were trained using GPU acceleration.}
\label{tab:trainingtimes}
\resizebox{0.5\linewidth}{!}{%
\begin{tabular}{cr}
\toprule
Model  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Training \\ Time\\ $[s/(districts \cdot splits)]$\end{tabular}}  \\
\hline
ARIMA  & 1.12                                                                                                           \\
HW-ES  & 0.63                                                                                                           \\
NBEATS & 40.6                                                                                                           \\
GWNet  & 0.49                                                                                                           \\
\bottomrule
\end{tabular}
}
\end{table}



